---
title: "S2 Appendix"
output: 
  pdf_document:
    toc: true
header-includes:
  - \maxdeadcycles=200
---
  \maxdeadcycles=200
\newcommand{\beginsupplement}{%
  \setcounter{table}{0}
  \renewcommand{\thetable}{A\arabic{table}}%
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{A\arabic{figure}}%
}

\beginsupplement
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load, include = F} 
library(data.table)
library(stringr)
all_model_files <- list.files(path = "brms_fits/")
age_model_names <- all_model_files[grepl("extra_age_", all_model_files, fixed = TRUE)]
age_models_path <-  paste0("brms_fits/", age_model_names)
plain_model_names <- all_model_files[grepl("plain_", all_model_files, fixed = TRUE)]
bug_names<- data.table(read.csv("translate_drug_bugs.csv"))
bug_names[, label := paste0(bac, drug)]

bugs <- bug_names[match(str_remove(str_remove(plain_model_names, ".rds"), "plain_"), label)]$Bacteria
drugs <- bug_names[match(str_remove(str_remove(plain_model_names, ".rds"), "plain_"),label)]$Antibiotic
combined_names <-bug_names$label

bug_drugs_dict <- read.csv("bug_names.csv")

```

# 1 - Country names

AT is	Austria, BE is Belgium, BG is Bulgaria, CY is Cyprus, CZ is Czechia, DE is Germany, DK is Denmark, EE is Estonia, EL is Greece, ES is Spain, FI is Finland, FR is France, HR is Croatia, HU is Hungary, IE is Ireland, IS is Iceland, IT is Italy, LI is Liechtenstein, LT is Lithuania, LU is Luxembourg, LV is Latvia, MT is Malta, NL is Netherlands, NO is Norway, PL is Poland, PT is Portugal, RO is Romania, SE is Sweden, SI is Slovenia and SK is Slovakia.

# 2 - Validation of incidence

Total BSI incidence in 2023 was compared to model predicted 2023 BSI incidence. Antibiotic groupings in the 2023 report were slightly different than in the more disaggregated 2015-2020 data used for predictions, so small differences in classification may exist, and they 2023 data is not age or sex stratified. 

Figure A1 shows the log error comparing estimated vs actual data. The subsequent figures (A2-A12) show the predictions against the data.

```{r overall_validation, echo=FALSE, fig.cap = paste0("Log error of predicted BSIs in 2023 compared to ECDC reported data. Colour indicates country. Dashed lines indicate -0.7 and 0.7, equating to ~ half and double the actual value."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/logerror.pdf"))
```



```{r validation_1, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point). A) ", bug_drugs_dict[1,"combo_name"], " B) ", bug_drugs_dict[2,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[2, "combo_name"],".pdf"))
```


```{r validation_2, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[3,"combo_name"], " B) ", bug_drugs_dict[4,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[4, "combo_name"],".pdf"))
```


```{r validation_3, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[5,"combo_name"], " B) ", bug_drugs_dict[6,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[6, "combo_name"],".pdf"))
```


```{r validation_4, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[7,"combo_name"], " B) ", bug_drugs_dict[8,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[8, "combo_name"],".pdf"))
```


```{r validation_5, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[9,"combo_name"], " B) ", bug_drugs_dict[10,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[10, "combo_name"],".pdf"))
```


```{r validation_6, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[11,"combo_name"], " B) ", bug_drugs_dict[12,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[12, "combo_name"],".pdf"))
```


```{r validation_7, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[13,"combo_name"], " B) ", bug_drugs_dict[14,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[14, "combo_name"],".pdf"))
```


```{r validation_8, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[15,"combo_name"], " B) ", bug_drugs_dict[16,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[16, "combo_name"],".pdf"))
```


```{r validation_9, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[17,"combo_name"], " B) ", bug_drugs_dict[18,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[18, "combo_name"],".pdf"))
```


```{r validation_10, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[19,"combo_name"], " B) ", bug_drugs_dict[20,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[20, "combo_name"],".pdf"))
```


```{r validation_11, echo=FALSE, fig.cap = paste0("Predicted BSIs in 2023 under fixed or linear trends (type, colour) compared to ECDC reported data (black point).A) ", bug_drugs_dict[21,"combo_name"], " B) ", bug_drugs_dict[22,"combo_name"],"." ), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/validation_inc_",bug_drugs_dict[22, "combo_name"],".pdf"))
```




# 3 - Including age/sex resistance rates

Total resistant BSIs per age and sex in 2030 were compared between the "base" model that assumed a constant proportion resistant across age and sexes, and the "agesex" model that allowed for variation in resistance by age and sex (see methods, Figure 1). The following plots (A13-A50) show a breakdown of the comparison by age and sex, and also by country. 


```{r comparison_1, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles. ", bugs[1], " ", drugs[1], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[1],".pdf"))
```


```{r comparison_2, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[2], " ", drugs[2], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[2],".pdf"))
```


```{r comparison_3, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[3], " ", drugs[3], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[3],".pdf"))
```

```{r comparison_4, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[4], " ", drugs[4], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[4],".pdf"))
```

```{r comparison_5, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[5], " ", drugs[5], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[5],".pdf"))
```

```{r comparison_6, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[6], " ", drugs[6], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[6],".pdf"))
```

```{r comparison_7, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[7], " ", drugs[7], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[7],".pdf"))
```

```{r comparison_8, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[8], " ", drugs[8], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[8],".pdf"))
```

```{r comparison_9, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[9], " ", drugs[9], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[9],".pdf"))
```

```{r comparison_10, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[10], " ", drugs[10], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[10],".pdf"))
```

```{r comparison_11, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[11], " ", drugs[11], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[11],".pdf"))
```

```{r comparison_12, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[12], " ", drugs[12], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[12],".pdf"))
```

```{r comparison_13, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[13], " ", drugs[13], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[13],".pdf"))
```

```{r comparison_14, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[14], " ", drugs[14], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[14],".pdf"))
```

```{r comparison_15, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[15], " ", drugs[15], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[15],".pdf"))
```

```{r comparison_16, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[16], " ", drugs[16], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[16],".pdf"))
```

```{r comparison_17, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[17], " ", drugs[17], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[17],".pdf"))
```

```{r comparison_18, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[18], " ", drugs[18], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[18],".pdf"))
```

```{r comparison_19, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[19], " ", drugs[19], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[19],".pdf"))
```

```{r comparison_20, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[20], " ", drugs[20], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[20],".pdf"))
```

```{r comparison_21, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[21], " ", drugs[21], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[21],".pdf"))
```

```{r comparison_22, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[22], " ", drugs[22], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[22],".pdf"))
```

```{r comparison_23, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[23], " ", drugs[23], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[23],".pdf"))
```

```{r comparison_24, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[24], " ", drugs[24], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[24],".pdf"))
```

```{r comparison_25, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[25], " ", drugs[25], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[25],".pdf"))
```

```{r comparison_26, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[26], " ", drugs[26], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[26],".pdf"))
```

```{r comparison_27, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[27], " ", drugs[27], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[27],".pdf"))
```

```{r comparison_28, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[28], " ", drugs[28], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[28],".pdf"))
```

```{r comparison_29, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[29], " ", drugs[29], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[29],".pdf"))
```

```{r comparison_30, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[30], " ", drugs[30], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[30],".pdf"))
```

```{r comparison_31, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[31], " ", drugs[31], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[31],".pdf"))
```

```{r comparison_32, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[32], " ", drugs[32], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[32],".pdf"))
```

```{r comparison_33, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[33], " ", drugs[33], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[33],".pdf"))
```

```{r comparison_34, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[34], " ", drugs[34], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[34],".pdf"))
```

```{r comparison_35, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[35], " ", drugs[35], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[35],".pdf"))
```

```{r comparison_36, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[36], " ", drugs[36], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[36],".pdf"))
```

```{r comparison_37, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[37], " ", drugs[37], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[37],".pdf"))
```

```{r comparison_38, echo=FALSE, fig.cap = paste0("Difference between ‘agesex’ and ‘base’ model projections in 2030. A positive difference indicates that using the ‘base’ model underestimates resistant BSIs compared to the ‘agesex’ model. A) by age and sex. The line depicts the median and the ribbon the 95% quantiles. The dashed line at 0 indicates no difference. B) by country. The solid line indicates no difference, and the dotted / dashed lines represent a 50 and 100% difference respectively. The dot depicts the median and the ribbon the 95% quantiles.  ", bugs[38], " ", drugs[38], "."), out.width="100%"}
knitr::include_graphics(path =paste0("plots_nw/supplement_2030_summary2_",plain_model_names[38],".pdf"))
```
